How does increasing $s$ and $k$ effect log normalising constant estimation

### 2023-04-09 src/naomi-simple_increase-s-k/increase-s-k.Rmd
Add s-k notebook #22

---
title: "How does increasing $s$ and $k$ effect log normalising constant estimation"
author:
- name: Adam Howes
output:
  bookdown::html_document2:
    toc: yes
    toc_float: yes
    toc_collapsed: yes
    df_print: paged
    code_folding: show
    theme: lumen
abstract: |
  **Background**

  **Task**
---

@@

```{r}
s1k2 <- readRDS("aghq-s1-k2.rds")
s2k2 <- readRDS("aghq-s2-k2.rds")
s3k2 <- readRDS("aghq-s3-k2.rds")
s4k2 <- readRDS("aghq-s4-k2.rds")
s5k2 <- readRDS("aghq-s5-k2.rds")
```

>>>>

---
title: "How does increasing $s$ and $k$ effect log normalising constant estimation"
author:
- name: Adam Howes
output:
  bookdown::html_document2:
    toc: yes
    toc_float: yes
    toc_collapsed: yes
    df_print: paged
    code_folding: show
    theme: lumen
abstract: |
  **Background** We have fit the Naomi model with a range of grids.

  **Task** How does changing the number of points per dimension $k$, or the number of dimensions of variation kept $s$ change the log normalising constant estimated?
---

@@

```{r}
s1k2 <- readRDS("depends/aghq-s1-k2.rds")
s2k2 <- readRDS("depends/aghq-s2-k2.rds")
s3k2 <- readRDS("depends/aghq-s3-k2.rds")
s4k2 <- readRDS("depends/aghq-s4-k2.rds")
s5k2 <- readRDS("depends/aghq-s5-k2.rds")
```
# Table processing

```{r}
lognormconsts <- c(
  s1k2$quad$normalized_posterior$lognormconst,
  s2k2$quad$normalized_posterior$lognormconst,
  s3k2$quad$normalized_posterior$lognormconst,
  s4k2$quad$normalized_posterior$lognormconst,
  s5k2$quad$normalized_posterior$lognormconst
)

df <- data.frame(
  s = 1:5,
  k = 2,
  lognormconst = lognormconsts
)

write_csv(df, "increase-s-k.csv")
```

# Visualisation

```{r}
ggplot(df, aes(x = s, y = lognormconst)) +
  geom_point() +
  facet_grid(k ~ .) +
  labs(x = "Dimensions kept of the PCA", y = "Log normalising constant") +
  theme_minimal()
```
